---
title: "Simulation"
author: "Jungang Zou"
date: "2/4/2020"
output: github_document
---

```{r setup, include=FALSE}
library(MASS)
library(glmnet)
library(tidyverse)
```



# correlation_process function
Do not call this function out of simulation function


```{r}

# this function is to calculate lasso function by cv
lasso_function = function(data, response){
  lambda_best = glmnet::cv.glmnet(x = data, y = response, alpha = 1, nfolds = 10) #cv to find best lambda
  lambda = lambda_best$lambda.min #best lambda
  lasso_best_fit = glmnet::glmnet(x = data, y = response, alpha = 1, nlambda = 1, lambda = lambda) #fit the lasso model
  lasso_best_fit
}

# this function is to calculate correlation matrix
correlation_process = function(parameters, type) {
  
  # function of density type
  correlation_density = function(parameters) {
    corr_matrix = parameters$corr_matrix
    strong = as.integer(parameters$strong * nrow(corr_matrix))
    weak_corr = as.integer(parameters$weak_corr * nrow(corr_matrix))
    weak_no_corr = as.integer(parameters$weak_no_corr * nrow(corr_matrix))
    density_num = as.integer(min(parameters$density, 1) * weak_corr * strong)
    for (i in (strong + 1):(strong + weak_corr)) {
      changed = FALSE
      for (j in 1:strong) {
        changed = rbernoulli(1)
        if (changed) {
          corr_matrix[i, j] = parameters$corr
          corr_matrix[j, i] = parameters$corr
          density_num = density_num - 1
          break
        }
      }
      if (!changed) {
         corr_matrix[i, 1] = parameters$corr
         corr_matrix[1, i] = parameters$corr
         density_num = density_num - 1
      }
    }
    changed_rate = max(density_num / (strong * weak_corr - weak_corr), 0)
    for (i in (strong + 1):(strong + weak_corr)) {
      for (j in 1:strong) {
        if (corr_matrix[i, j] == 0.5) {
          next
        }
        changed = rbernoulli(1, changed_rate)
        if (changed) {
          corr_matrix[i, j] = parameters$corr
          corr_matrix[j, i] = parameters$corr
          density_num = density_num - 1
        }
      }
    }
    return(corr_matrix)
  }
  
  # function of unique correlation.
  correlation_unique = function(parameters) {
    corr_matrix = parameters$corr_matrix
    strong = as.integer(parameters$strong * nrow(corr_matrix))
    weak_corr = as.integer(parameters$weak_corr * nrow(corr_matrix))
    weak_no_corr = as.integer(parameters$weak_no_corr * nrow(corr_matrix))
    for (i in (strong + 1):(strong + weak_corr)) {
      changed = FALSE
      for (j in 1:strong) {
        changed = rbernoulli(1)
        if (changed) {
          corr_matrix[i, j] = parameters$corr
          corr_matrix[j, i] = parameters$corr
          break
        }
      }
      if (!changed) {
         corr_matrix[i, 1] = parameters$corr
         corr_matrix[1, i] = parameters$corr
      }
    }
    return(corr_matrix)
  }
  
  if (type == "density") {
    return(correlation_density(parameters))
  }
  
  if (type == "unique") {
    return(correlation_unique(parameters))
  }
  
}

```





# Simulation Function:

input:

* n(required) : #sample
* p(required) : #feature
* percentage(required): vector of length 3, percentage of strong, weak_correlated and weak data, must be positive, not need to be sum up to 1
* c : to calculate the zone of beta, if beta is specified, this parameter has no use
* mu : the mean of strong and weak_correlated data
* sigma : the covariance of strong and weak_correlated data
* beta : true beta. If beta is not specified, beta will be sampled by formulas of c
* seed : set the random seed.
* error_sigma : the variance of error term
* correlation : the correlation between strong variables and weak_corr variables
* type : the type of correlation, you can specify it in {"unique", "density"}
* weak_corr_density : the density of correlation. The number of correlation will be density * #strong * # weak_corr. Randomly select correlation.  If type is not "density", this parameter will be no use.

output:

* beta : a tibble consist of true beta, lr beta, step beta, lasso beta, beta type
* data : the simulated data
* response : the simulated response data
* c : c is specified or calculated
* percentage: scaled percentage
* lr_model : the fitted linear regression model
* step_model : the fitted stepwise forward model
* lasso_model: the fitted lasso model
* cov_matrix: covariance matrix 

The relationship between c and beta:
If c is specified and beta is NULL, then the function will calculate different zone for beta, and simulate beta from the calculated zone by percentage.
If beta is specified, c will be no use. And new c will be calculate in function.

Correlation type:
If type is "unique", each weak_corr variable will be randomly correlate to only 1 strong variables.
If type is "density", each weak_corr variable will be randomly correlate to at least 1 strong variables. All the correlation will be sum up to weak_corr_density * #strong * #weak_corr.

```{r}


# This is the main function of simulation
simulation <- function(n, p, percentage, c = 1, mu = 1, sigma = 0.5, beta = NULL, seed = 100, error_sigma = 1, correlation = 0.5, type = "density", weak_corr_density = 0.5) {
  set.seed(seed) 
  
  # check input
  if (length(percentage) != 3) {
    stop("please send the 3 samples percentage")
  }
  if (p > n) {
    warning("#Features are more than #samples")
  }
  if (length(beta) > 0 && length(beta) != p) {
    stop("#Features is not consistent with #coefficient")
  }
  if (sum(percentage < 0)) {
    stop("percentage cannot be negative")
  }
  if (weak_corr_density < 0 || weak_corr_density > 1) {
    stop("weak_corr_density must be in [0, 1]")
  }
    
  # scale percentage
  strong = percentage[1] / sum(percentage)
  weak_corr = percentage[2] / sum(percentage)
  weak_no_corr = percentage[3] / sum(percentage)
  corr_feature = as.integer((strong + weak_corr) * p)
  no_corr_feature = p - corr_feature
  
  num_corr_feature = as.integer(weak_corr_density * weak_corr * strong * p * p)
  
  sigma_matrix = matrix(rep(0, p * p), nrow = p, ncol = p)
  diag(sigma_matrix) = 1
  
  parameters = list(corr_matrix = sigma_matrix, strong = strong, weak_corr = weak_corr, weak_no_corr = weak_no_corr, density = weak_corr_density, corr = correlation)
  
  sigma_matrix = correlation_process(parameters, type)
  #for (i in 1:as.integer(strong * p)) {
  #  sigma_matrix[i][i + as.integer(strong * p)] = 0.5
  #  sigma_matrix[i + as.integer(strong * p)][i] = 0.5
  #}
  #print(sigma_matrix)
  
  # simulate correlated data from multivariate Guassian distribution
  #print(correlation_process(parameters, "density"))
  #return(correlation_process(parameters, "density"))
  #print(sigma_matrix * sigma)
  #return(sigma_matrix)
  
  data = mvrnorm(n = n, mu = rep(mu, p), Sigma = sigma_matrix * sigma, tol = 1)
  
  # simulate uncorrelated data
  #for (i in 1:no_corr_feature) {
  #  no_corr = rnorm(n, mu, sigma)
  #  data = cbind(data, no_corr)
  #}
  
  # set the variable names
  data_columns_names = paste("V", 1:p, sep = "")
  colnames(data) <- data_columns_names
  
  
  # if beta is specified,  calculate c
  if (length(beta) != 0) {
    strong_beta = sort(beta, decreasing = TRUE)[as.integer(strong * p) + 1]
    c = strong_beta / sqrt(log(p) / n)
  }
  
  # if beta is not specified, simulate beta by c
  if (length(beta) == 0) {
    strong_beta = runif(as.integer(strong * p), min = c * sqrt(log(p) / n), max = c * sqrt(p / n))
    
    weak_corr_beta = runif(as.integer(weak_corr * p), min = 0, max = c * sqrt(log(p) / n))
    
    weak_beta = runif(p - as.integer(strong * p) - as.integer(weak_corr * p), min = 0, max = c * sqrt(log(p) / n))
    
    beta = c(strong_beta, weak_corr_beta, weak_beta)
    
    # randomly make some beta negative 
    beta_sign = runif(length(beta), -1, 1)
    beta_sign = beta_sign / abs(beta_sign)
    beta = beta * beta_sign
  }
  
  # calculate response variable
  error_term = rnorm(n, mean = 0, sd = error_sigma)
  response = data %*% beta + error_term
  
  
  # regression
  lr = lm(response ~ data)
  step_lr = step(lm(response ~ data), direction = "forward")
  lasso = lasso_function(data, response)

  
  # collect beta as tibble
  beta_result = tibble(
      "true beta" = beta,
      "lr coefficient" = coefficients(lr)[2:length(coefficients(lr))],
      "step coefficient" = coefficients(step_lr)[2:length(coefficients(step_lr))],
      "lasso coefficient" = as.vector(coefficients(lasso))[2:length(coefficients(lasso))],
      "type" = c(rep("strong", as.integer(strong * p)), rep("weak_corr", as.integer(weak_corr * p)), rep("weak", p - as.integer(strong * p) - as.integer(weak_corr * p)))
      ) %>% 
    replace(is.na(.), 0)
  
  # collect output
  result = list(beta = beta_result, data = data, response = response, c = c, percentage = c(strong, weak_corr, weak_no_corr), lr_model = lr, step_model = step_lr, lasso_model = lasso, cov_matrix = sigma_matrix * sigma)
  return(result)
}


## try to change the maximum of beta to 10

step_strong_F1 = c()

for (i in 20:30) {
  #  change parameter numbers
  a = simulation(100, i, c(1,3,2))
  ## to see the accuracy of the two selection methods
  ## check the selected accuracy
  step_strong_index = abs(a$beta$`lasso coefficient`)>0
  type = a$beta$type
  step_recall = sum(type[step_strong_index] == "strong")/sum(type == "strong")
  step_prec = sum(type[step_strong_index] == "strong")/length(step_strong_index)
  step_strong_F1 =c(step_strong_F1,2/(1/step_recall+1/step_prec)) 
}


lasso_strong_F1 = c()

for (i in 20:30) {
  #  change parameter numbers
  a = simulation(100, i, c(1,3,2))
  ## to see the accuracy of the two selection methods
  ## check the selected accuracy
  lasso_strong_index = abs(a$beta$`lasso coefficient`)>0
  type = a$beta$type
  lasso_recall = sum(type[lasso_strong_index] == "strong")/sum(type == "strong")
  lasso_prec = sum(type[lasso_strong_index] == "strong")/length(step_strong_index)
  lasso_strong_F1 =c(lasso_strong_F1,2*lasso_prec * lasso_recall / (lasso_prec + lasso_recall)) 
}


plot(20:30, step_strong_F1)
plot(20:30,lasso_strong_F1)

a

## also could tuning other parameters, like sample size and percentage
```
